# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data
```{r}
amd<-read.csv("./activity.csv",header=T,sep=",")
str(amd)
```
### Process/transform the date field in Activity monitoring data into a date format suitable for your analysis
```{r}
amd$date<-as.Date(amd$date)
str(amd)
```

## What is mean total number of steps taken per day?
### Make a histogram of the total number of steps taken each day
```{r,results='hide'}
amdsteps<-tapply(amd$steps,amd$date,sum)
```
```{r,echo=TRUE}
library(reshape2)
amdmelt<-melt(amdsteps)
names(amdmelt)<-c("date1","sum1")
head(amdmelt)
```
```{r}
library(ggplot2)
qplot(data=amdmelt,sum1,fill=date1,binwidth=1000)
```
### Calculate and report the mean and median total number of steps taken per day
```{r,echo=TRUE}
tapply(amd$steps,amd$date,mean)
tapply(amd$steps,amd$date,median)

```



## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
